### 2018-04-25 Paper/jaccardbaetica.tex
add form

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index. The formula can be described as follows

(FORMULA Y DESCRIPCIÓN)

This method was performed to measure the overlap between different samples of sets \citep{morisita_measuring_1959, horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

>>>>

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index \citep{morisita_measuring_1959, horn_measurement_1966}. This method was performed to measure the overlap between different samples of sets. Generally, it describes the dissimilarity between the system of two communities based on the idea of inverse correlation between diversity and species (CITAR AQUI MANGURRIAN)

The formula can be described as follows \citep{magurran_measuring_2013}:

\begin{equation}
D(MH) = 1- \frac{2 \sum(a_{i} \cdot b_{i})}{(d_{a} + d_{b}) \cdot (N_{a} \cdot N_{b})}
\end{equation} \\

$d_{a}$ and $d_{b}$ are given by the following equation:

\begin{equation}
d_{a} = \frac{\sum a_{i}^{2}}{N_{a}^{2}} 
\end{equation} \\

where $N_{a}$ is the total number of stamps in workshop A; $N_{b}$ is the total number of stamps in workshop B; $a_{i}$ is the number of different stamps for workshop A and $b_{i}$ is the number of different stamps for workhop B.
